\begin{thebibliography}{100}

\bibitem{linetypes}
  	Mark E. Shoulson
 	The pyBlazon wiki, 
 	https://code.google.com/p/pyblazon/wiki/PartyPer , 
 	Febuary 4th 2010


\bibitem{ruleofTincture}
	Michel Pastoureau. 
	Heraldry, Its Origins and Meaning.
	New Horizons. 
	Published in 1996, translated in 1997.


\bibitem{countercharge}
	The language of Helaldry.
	http://www.obcgs.com/charge1.jpg

\bibitem{rampant}
	Author: Sodacan,  
	The Wikimedia Commons,
	Description: A Heraldic Lion in Rampant Attitude
	http://upload.wikimedia.org/wikipedia/commons/7/75/Lion\_Rampant.svg
	13 April 2009

\bibitem{passant}
	Author: Sodacan,
	The Wikimedia Commons, 
	Description: A Heraldic Lion in Passant Attitude, 
	http://upload.wikimedia.org/wikipedia/commons/f/f3/Lion\_Passant.svg ,
	13 April 2009
	
\bibitem{fessways}
	Adapted from: 
	Phelan and Vanor , 
	March 1 1989, 
	http://khevron.tripod.com/armorial/awards.html


\bibitem{bob}
	Michel Pastoureau. 
	Heraldry, Its Origins and Meaning.
	New Horizons. 
	Published in 1996, translated in 1997.


\bibitem{oxford}
	Thomas Woodcock and John Martin Robinson, 
	The Oxford Guide to Heraldry, 
	The Oxford University Press, 
	Reissued in 2001


\bibitem{luke}
	Luke Torjussen, 
	Translating Blason into Coats of Arms, 
	May 2012

\bibitem{dragon}
	Compilers principles, Techniques, \& Tools, 
	Alfred V. Aho, Monica S. Lam, Ravi Sethi, Jeffrey D. Ullman, 
	Second edition,  Published by Pearson, 
	2007 

\bibitem{2dforyou}
	Keven Lindsey,
	2002,
	http://www.kevlindev.com/geometry/index.htm


\bibitem{Ace}
	The ace editor home page, 
	accessed 29th April 2013, 
	http://ace.ajax.org/

\bibitem{font}
	Medieval Sharp Font, 
	Google, 
	http://fonts.googleapis.com/css?family=MedievalSharp


\bibitem{proj}	
	Luke Torjussen,
	Translate Blazon into Coats of Arms,
	2012,
	http://1.shielddrawing.appspot.com/


\bibitem{tom}
	Tom Heyes, 
	Blazon Online, 
	2013, 
	http://tomhey.es/blazon

\end{thebibliography}