\chapter{Conclusion}

This report has thoroughly described the development of this Blazon parsing web application, from researching the problem domain to detailed pseudo code of the key algorithms used in the final implementation. 

Having read this document a comprehensive understanding of the Blazon Languge should have been obtained.  A brief description of Lexical analysis, Parsing and Context Free Grammars was given in the context of applying each to Blazon. 

A description of how the graphical aspect of the application was developed and the algorithm for partitioning fields was given.     

An oversight of the data structures was presented and a thorough description of testing methods that were used and an evaluation of completeness was given by bench marking against a similar application. 

\section{Attainment}

A lot of the initial goals set out at the beginning of the project have been met.  The application correctly parses complex Blazon sentences and can graphically render a large subset of the language.  Compared to a previous application this implementation runs a lot faster and covers a larger subset of the language. 

\section{Continuing the Project}
If the project were to be continued in the future the main priority would be to address the limitations fo the project starting with the rendering of semi-formal charges.  The project is live\cite{tom} and probably will be improved in the future.  

Another limitation of the project to be addressed is the small number of geometric charges defined which is not a hard issue to resolve but will require a significant amount of time to implement. 

\section{Final Notes}

The project has been enjoyable to develop and Blazon is a rather fun problem domain.  A lot of skills were learned in the implementation of the project such as \emph{JavaScript} development and HTML5 Canvas functions.  A lot of information regarding the theory of computation was learned and the entire language of Blazon was researched and understood. 
